\documentclass[a4paper]{article}
\usepackage[margin=1in]{geometry}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage[auth-sc,affil-sl]{authblk}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{setspace}

\title{User Interface Evaluation of the CP's Website\\ (Proposal)}
\author[1]{Luís  Cruz}
\affil[1]{MAP-i\\ Joint Doctoral Programme in Computer Science}
\date{January 4, 2014}

\newcommand{\myrule}[1]{\rule{#1}{0.45pt}}
\newcommand{\tally}{\emph{Tally}\hfill{}}
\newcommand{\ratingMark}{
  \hfill{}\mbox{
    {\footnotesize Disagree $\bigcirc \bigcirc \bigcirc \bigcirc \bigcirc$ Agree}
    }
}


\begin{document}

{\Large
Post-Test Questionnaire\footnote{Adapted from \textit{AIR, Human Factors and Research Design group}'s work.}
}
\vfill
CP.pt Usability Test

MAP-i Doctoral Programme

Responsible Moderator: Luís Cruz

22 January 2014

\vfill

Participant ID: \myrule{2cm}

Date: \myrule{2cm}

Time: \myrule{2cm}

\vfill

For our last activity I'm going to give you a short questionnaire that I would like you to fill out. The questionnaire will give you a series of statements about the CP.pt Web site. I would like you to rate your agreement with each statement.

For each statement, please circle a number to indicate the level to which you agree with each statement. If you feel a statement isn't relevant to your experiences with the Web site, please feel free to skip it.

\vfill

\begin{enumerate}
    \item The homepage is attractive   \ratingMark                     

  \item The overall site is attractive  \ratingMark

  \item The site's graphics are pleasing  \ratingMark                        

  \item The site has a good balance of graphics versus text  \ratingMark                        

  \item The colors used throughout the site are attractive  \ratingMark                        

  \item The typography is attractive  \ratingMark                        

  \item[]                          

  \item The homepage's content makes me want to explore the site further  \ratingMark                        

  \item It is easy to find one's way around the site  \ratingMark                        

  \item You can get information quickly  \ratingMark                        

  \item It is fun to explore the site  \ratingMark                        

  \item It is easy to remember where to find things  \ratingMark                        

  \item Information is layered effectively on different screens  \ratingMark                        

  \item[]                          

  \item The homepage is attention-getting  \ratingMark                        

  \item Information is easy to read  \ratingMark                        

  \item Information is written in a style that suits me  \ratingMark                        

  \item Screens have the right amount of information  \ratingMark                        

  \item The site effectively communicates the company's image  \ratingMark                        

  \item Information is relevant  \ratingMark                        

  \item[]                         
\begin{samepage}
  \item The site is designed with me in mind  \ratingMark                        

  \item The site's content interests me  \ratingMark                        

  \item The site's content would keep me coming back  \ratingMark                        

  \item The site has characteristics that make it especially appealing  \ratingMark                        

  \item The site reflects progressive, leading edge design  \ratingMark                        

  \item The site is exciting  \ratingMark                        

  \item[]      
  \end{samepage}                    

\begin{samepage}
  \item The site is well-suited to first-time visitors  \ratingMark                        

  \item Ths site is well-suited to repeat visitors  \ratingMark                        

  \item The site has a clear purpose  \ratingMark                        

  \item It is always clear what to do next  \ratingMark                        

  \item It is clear how screen elements work  \ratingMark                        

  \item Mistakes are easy to correct  \ratingMark   
  \end{samepage}
\end{enumerate}
  

~

And that's it! Please return this questionnaire to the moderator.

Thank you for your collaboration!

\end{document}
